---
title: 'MATH 437 HW2'
author: "Drew Remmenga"
output:
  pdf_document: default
  html_notebook: default
---
1.a.
Singular values are $\sigma_{1} =4$,$\sigma_{2} =2$,$\sigma_{3} =1$, and $\sigma_{4} =5$.
1.b. 
Singular values are $\sigma_{1} =1$,$\sigma_{2} =1$,$\sigma_{3} =1$, and $\sigma_{4} =1$.
1.c. 
$A=\begin{bmatrix} 1  & 0 & 0\\ 0 & 0 & 1\\0& 1& 0\\\end{bmatrix}$ A is different from the identity and is orthogonal. 
2.a.
$\hat{\beta}=(A^{T}\Sigma^{-1}A)^{-1}A^{T} \Sigma^{-1}y$
2.b.
mean=$\hat{\beta}=(A^{T}\Sigma^{-1}A)^{-1}A^{T}\Sigma^{-1}A \beta$
$E(\hat{\beta})=\beta$
$Cov(\hat{\beta})=(A^{T}\Sigma^{-1}A)^{-1}$
2.c.
$Cov(r)=I-A(A^{T}\Sigma^{-1}A)^{-1}A^{T}\Sigma^{-1}\Sigma(I-A(A^{T}\Sigma^{-1}A)^{-1}A^{T}\Sigma^{-1})$
3.a.
$=\begin{bmatrix} a_{1,1}  & a_{1,2}\\ a_{2,1} & a_{2,2} \\a_{1,1}  & a_{1,2}\\ a_{2,1} & a_{2,2}\\\end{bmatrix}$
3.b.
$\begin{bmatrix} a_{1,1}  & a_{1,1} & a_{1,1} & a_{1,2} & a_{1,2} & a_{1,2}\\ a_{2,1} & a_{2,1} & a_{2,1} & a_{2,2} & a_{2,2} & a_{2,2}\\\end{bmatrix}$
3.c.
$\begin{bmatrix} a_{1,1}  & a_{1,2} & 0 & 0\\a_{2,1} & a_{2,2} & 0 & 0 \\0&0&a_{1,1}&a_{1,2}\\0&0&a_{2,1}&a_{2,2}\\\end{bmatrix}$
3.d.
$\begin{bmatrix} a_{1,1}  & 0&a_{1,2} & 0\\0 & a_{1,1} & 0 & a_{1,2} \\a_{2,1}&0&a_{2,2}&0\\0&a_{2,1}&0&a_{2,2}\\\end{bmatrix}$
3.e.
$\begin{bmatrix} a_{1,1}a_{1,1}  & a_{1,1}a_{1,2}&a_{1,2}a_{1,1} & a_{1,2}a_{1,2}\\a_{1,1}a_{2,1} & a_{1,1}a_{2,2} & a_{1,2}a_{2,1} & a_{1,2}a_{2,2} \\a_{1,1}a_{2,1}&a_{2,1}a_{1,2}&a_{2,2}a_{1,1}&a_{1,2}a_{2,2}\\a_{2,1}a_{2,1}&a_{2,1}a_{2,2}&a_{2,2}a_{2,1}&a_{2,2}a_{2,2}\\\end{bmatrix}$
3.f.
let A=$\begin{bmatrix} 1 & 2 \\ 3 & 5 \\\end{bmatrix}$
then $(A\otimes A)(I\otimes A)=\begin{bmatrix} 7 & 18 & 21 & 54 \\ 12 & 31 & 36 & 93 \\ 14 & 36 & 35 & 90 \\ 24 & 62 & 60 & 155 \\\end{bmatrix}$
4.a.
$E(Y) = (0,0,0,0)^{T} $
4.b.
$Var(Y) = (2, 2,1,1)^{T}$
4.c.
$E(U) = \begin{bmatrix}0&0\\0&0\\\end{bmatrix}$
$Var(U) = \begin{bmatrix}2&2\\1&1\\\end{bmatrix}$
5.a.
x1=N(1,1)
x2=N(1,5)
5.b.
```{r}
sigma <- matrix(c(1,-2,-2,5),nrow=2)
mu=c(1,1)
x = matrix(c(1,0,1,-1),nrow=2)
x%*%mu
t(x)%*%sigma%*%x
```
5.c.
```{r}
x = matrix(c(1,1,1,-1),nrow=2)
x%*%mu
t(x)%*%sigma%*%x
```
5.d.
new $\mu=\begin{bmatrix}a_{1,1}&a_{1,2}\\a_{2,1}&a_{2,2}\\\end{bmatrix}\mu$
new $\sigma= (\begin{bmatrix}a_{1,1}&a_{1,2}\\a_{2,1}&a_{2,2}\\\end{bmatrix})^{T}\Sigma\begin{bmatrix}a_{1,1}&a_{1,2}\\a_{2,1}&a_{2,2}\\\end{bmatrix}$
5.e.
new $\mu=\begin{bmatrix}a_{1,1}&a_{1,2}\\a_{2,1}&a_{2,2}\\\end{bmatrix}b\mu$
new $\sigma= (\begin{bmatrix}a_{1,1}&a_{1,2}\\a_{2,1}&a_{2,2}\\\end{bmatrix}b)^{T}\Sigma\begin{bmatrix}a_{1,1}&a_{1,2}\\a_{2,1}&a_{2,2}\\\end{bmatrix}b$
5.f.
$a=1,b=-1$
6.a.
Since the vector is positive and the sigma matrix is always semi definite the matrix $a^{T}\Sigma a$ is always positive definite.